### 2016-12-13 poster/poster.tex
poster tweaks and images added

%% Box 2
\headerbox{Dataset}{name=intro1,column=0,row=0.40, span=1}{
\color{black}\vspace*{3pt}
English GigaWord corpus (LDC), LA Times from 2009 \vspace*{10pt}
\\
\hspace*{5pt}
\begin{tabular}{cc}
\parbox{0.27\textwidth}{
\vspace*{-0pt}
%\includegraphics[width=.24\columnwidth]{graphics/newspaper.pdf}
\includegraphics[width=.24\columnwidth]{graphics/latimes.jpg}

@@

%% Box 2
\headerbox{Model specifics}{name=intro1,column=0,row=0.67, span=1}{
\color{black}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item Words are embedded in the hidden sized space: $\mathbb{N}^{35642} \rightarrow \mathbb{R}^{256}$.
\item Embedded words are run through the RNN: $w_i = f(w_0^{i-1},\Theta)$.
\item Cross-entropy loss is used to learn the parameters.
\end{itemize}
\begin{center}
\begin{tabular}{cc}
\textbf{hyperparam} & \textbf{value} \\\hline
RNN type & \texttt{LSTM} \\
hidden size & $256$ \\
optimizer & \texttt{AdamOptimizer} \\
learning rate & $0.003$ \\
batch size & 25 \\

@@

%% BOX 0
\headerbox{Hardware}{name=methods,column=1,row=0.00,span=1}{
\vspace{0.5em}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{CPU}: Intel Core i7-5930K, 6 core, 12 thread (3.5 GHz)
\item \textbf{Memory}: G.SKILL Ripjaws 4 Series (8 x 8 GB)
\item \textbf{GPU}: GeForce GTX TITAN X (2 x 12 GB)
\end{itemize}

TODO: maybe convert into methodology section -- what experiments we ran
(until convergence, single epoch, single batch)
}

\headerbox{Logos \& Graphs}{name=results,column=1,row=0.30, span=1}{
%\includegraphics[width=.3\columnwidth]{graphics/TensorFlow.png}
%\includegraphics[width=.3\columnwidth]{graphics/theano.jpeg}
%\includegraphics[width=.3\columnwidth]{graphics/DyNet.pdf}

Replacement image here?

% placeholdering for more appropriate graph
\begin{center}
Total runtime on various subtasks, using one GPU:
\end{center}

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & x \\
Test batch & < 1s & $<$1s & x \\
\end{tabular}
\egroup

@@

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.65, span=1}{

\setlength{\extrarowheight}{3pt}
\begin{tabularx}{\textwidth}{l|X|X|X}
\textbf{Framework}  & \textbf{Pros} & \textbf{Cons} \\
\hline
TensorFlow   & Easy to use; good support for RNNs and language models &
    Symbolic computation graph is hard to debug; seems slower than others \\
\hline
Theano  & ``Lower level'' operations $\rightarrow$ highly customizable &
    No built-in support for RNNs (either need to implement or use a wrapper like Keras)  \\
\hline
DyNet   & Allows flexible models that change during computation & Less documentation and support; fragile dependencies  \\
\end{tabularx}
}

>>>>

%% Box 2
\headerbox{Dataset}{name=intro1,column=0,row=0.415, span=1}{
\color{black}\vspace*{3pt}
English GigaWord corpus (LDC), LA Times from 2009 \vspace*{10pt}
\\
\hspace*{5pt}
\begin{tabular}{cc}
\parbox{0.27\textwidth}{
\vspace*{-0pt}
%\includegraphics[width=.24\columnwidth]{graphics/newspaper.pdf}
\includegraphics[width=.24\columnwidth]{graphics/latimes.jpg}

@@

%% Box 2
\headerbox{Model specifics}{name=intro1,column=0,row=0.7, span=1}{
\color{black}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item Words are embedded in the hidden sized space: $\mathbb{N}^{35642} \rightarrow \mathbb{R}^{256}$.
\item Embedded words are run through the RNN: $w_i = f(w_0^{i-1},\Theta)$.
\item Cross-entropy loss is used to learn the parameters.
\end{itemize}
\begin{center}
\begin{tabular}{cc}
\textbf{hyperparam} & \textbf{value} \\\hline
RNN type & \texttt{LSTM} \\
hidden size & $256$ \\
optimizer & \texttt{AdamOptimizer} \\
learning rate & $0.003$ \\
batch size & 25 \\

@@

%% BOX 0
\headerbox{Hardware}{name=hardware,column=1,row=0.00,span=1}{
\vspace{0.5em}
\hspace{-15pt}
\begin{tabular}{cc}
\parbox{0.85\textwidth}{
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{CPU}: Intel Core i7-5930K, 6 core, 12 thread (3.5 GHz)
\item \textbf{Memory}: G.SKILL Ripjaws 4 Series (8 x 8 GB)
\item \textbf{GPU}: GeForce GTX TITAN X (2 x 12 GB)
\end{itemize}\vspace*{35pt}
} & \hspace*{-10pt}
\includegraphics[scale=.1]{graphics/titanx.png}\vspace*{-35pt}
\end{tabular}
% TODO: maybe convert into methodology section -- what experiments we ran (until convergence, single epoch, single batch)
}
\headerbox{Benchmarking strategy}{name=methods,column=1,row=0.1965, span=1}{
\vspace{5pt}
\begin{itemize}
\item \textbf{Timing}:\\convergence, single epoch, single batch
\item \textbf{GPU Profiling}:\\overall, matrix multiply, specific GPU metrics
\end{itemize}
\vspace{5pt}
}

\headerbox{Runtime}{name=results,column=1,row=0.415, span=1}{
%\includegraphics[width=.3\columnwidth]{graphics/TensorFlow.png}
%\includegraphics[width=.3\columnwidth]{graphics/theano.jpeg}
%\includegraphics[width=.3\columnwidth]{graphics/DyNet.pdf}

% placeholdering for more appropriate graph
\includegraphics[scale=.07]{graphics/hourglass.jpg}\vspace*{-35pt}
\begin{center}
\textbf{Total runtime on various subtasks, using one GPU:}
\end{center}

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & x \\
Test batch & < 1s & $<$1s & x \\
\end{tabular}
\egroup
\vspace{5pt}
}

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.70, span=1}{
\setlength{\extrarowheight}{3pt}
\begin{tabularx}{\textwidth}{l|X|XX}
\textbf{Framework}  & \textbf{Pros} & \textbf{Cons} \\
\hline
TensorFlow   & Easy to use; good support for RNNs and language models &
    Symbolic computation graph is hard to debug; seems slower than others \\
\hline
Theano  & ``Lower level'' operations $\rightarrow$ highly customizable &
    No built-in support for RNNs (unless using wrapper like Keras)  \\
\hline
DyNet   & Allows flexible models that change during computation & Less documentation and support; fragile dependencies  \\
\end{tabularx}

@@
